---
title: "Total Public Complaints Filed with The Independent Police Review Director (O.I.P.R.D.) "
subtitle: "Broken Down by Complaints that were Investigated and Not Investigated"
author: 
  - Sarah Ding
thanks: "Code and data are available at: https://github.com/sarahdingg/sta_analysis."
date: 27 September 2024
date-format: long
abstract: "This paper examines the different types of public complaints filed with the police, the dataset is obtained from Open Data Toronto (@opendatatoronto), which includes total number of complaints from 2014 to 2023. The complaints are categorized into different types and whether if they are investigated by the police. The paper aims to explore the type of complaint that is most responded by the police, drawing conclusions that complaints about less serious conducts are investigated the most, and complaints that are not in public interest are not investigated the most."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)
library(ggplot2)
library(scales)
```

# Introduction

You can and should cross-reference sections and sub-sections. We use @citeR

The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

We first graph the mean of the total number of complaints for each subtype (@fig-times-mean) throughout the years.


```{r}
#| label: fig-times-mean
#| fig-cap: Number of Complaints filed under Different Subtypes
#| echo: false
#| warning: false
#| message: false

#Load Data
analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

ggplot(analysis_data, aes(x = SUBTYPE, y = COUNT_, fill = SUBTYPE)) +
  geom_bar(stat = "identity", width = 0.7) +
  scale_fill_brewer(palette = "Set3") +
  theme_minimal() +
  labs(title = "Total Complaints by Complaint Subtypes",
      x = "Complaint Subtypes",
      y = "Total Complained Filed") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(labels = comma)
```

Talk way more about it...

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

```{=tex}
\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}
```
We run the model in R [@citeR] 

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

Our results are summarized in





# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {.unnumbered}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

 we implement a posterior predictive check. This shows...

 we compare the posterior with the prior. This shows...



## Diagnostics



\newpage

# References
